The Evolution of Phenotypically Invariant Genetic Networks

### 2017-10-13 kalman_walk_paper.tex
minor edits from meeting

TALK ABOUT MINIMALITY

We refer to $\calA(\Sys_0)$ as the set of all systems equivalent to $\Sys_0$, regardless of dimension:
\begin{equation} \label{eqn:equivalence}
  \begin{aligned}
    \calA(\Sys_0) 
      &= \left\{
        (A,B,C) : C e^{At} B = C_0 e^{A_0 t} B_0 \; \text{for}\; t \ge 0 
      \right\}  \\
      &= \left\{
        (A,B,C) : C A^r B = C_0 A_0^r B_0 \; \text{for}\; 1 \le r \le n-1 
      \right\} .
  \end{aligned}
\end{equation}
Equivalence of the two characterizations follows from the Cayley-Hamilton theorem.

>>>>

It turns out that in general, there are more degrees of freedom,
except if the system is \emph{minimal} -- meaning, informally, that it uses the smallest possible number of components
to achieve the desired dynamics.
Results in system theory show that any system can be realized in a particular minimal dimension
(the dimension of the kryptotype, $n_\text{min}$),
and that any two phenotypically equivalent systems of dimension $n_\text{min}$ are related by a change of coordinates.

If the system is not minimal, then the Kalman decomposition tells us XXX

We refer to $\calA(\Sys_0)$ as the set of all systems equivalent to $\Sys_0$, regardless of dimension:
\begin{equation} \label{eqn:equivalence}
  \begin{aligned}
    \calA(\Sys_0) 
      &= \left\{
        (A,B,C) : C e^{At} B = C_0 e^{A_0 t} B_0 \; \text{for}\; t \ge 0 
      \right\}  .
  \end{aligned}
\end{equation}
